### 2020-08-31 thesis/thesis.tex
re pronoums
small fixes

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%         English Abstract                        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\SetAbstractEnName{{Abstract}}%
\SetAbstractEnText{Connectivity conservation science, whose goal is to preserve the continuity of habitat throughout a given landscape, proceeds by identifying priority areas given the current configuration of the landscape. However, current connectivity conservation planning methods often do not take into account risks associated with future land use and climate change, and often do not confront the results of the prioritization with the priorities perceived by stakeholders. In this thesis, we attempted to remedy those two issues in the context of an ongoing effort of connectivity conservation planning for the region of Montérégie in Southern Québec, Canada. In the first chapter, we built on past work of connectivity modelling using circuit theory in the region and complemented it with land use and climate change modelling that uses a combination of statistical modelling and MCMC-based simulations. Models trained on past land use data were used to project future land use changes and estimate future changes in potential functional connectivity for 5 different umbrella species. In a second chapter, we integrate these results with the perceived conservation priorities in the region. We conducted a day-long workshop with stakeholders involved in the ongoing connectivity conservation planning effort in the region and collected information on landscape features considered “core” and “linkages” priority areas. We showed the importance of considering land use changes to produce a resilient network of protected areas and highlight the need for a multi-stakeholder approach in the definition of conservation scenarios and the identification of regional priorities.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%         French Abstract                         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\SetAbstractFrName{{Abr\'{e}g\'{e}}}%
\SetAbstractFrText{La science de la conservation de la connectivité, dont le but est de préserver la continuité de l'habitat dans un paysage donné, procède par l'identification des zones prioritaires compte tenu de la configuration actuelle du paysage. Toutefois, les méthodes actuelles de planification de la conservation de la connectivité ne tiennent souvent pas compte des risques associés aux changements futurs d'utilisation des terres, et vont rarement jusqu'à confronter les résultats de la priorisation avec les priorités perçues par les parties prenantes. Dans cette thèse, nous avons tenté de remédier à ces deux problèmes dans le cadre d'un effort continu de planification de la conservation de la connectivité pour la région de la Montérégie, dans le sud du Québec, au Canada. Dans le premier chapitre, nous nous sommes appuyés sur les travaux antérieurs de modélisation de la connectivité basés sur la théorie des circuits dans la région et nous les avons complétés par une modélisation de l'utilisation des terres et du changement climatique qui utilise une combinaison de modélisation statistique et de simulations à base de chaînes Markov Monte Carlo. Le modèle construit à partir des données d'utilisation des terres passées ont été utilisés pour projeter les changements futurs d'utilisation des terres et estimer les changements futurs de la connectivité fonctionnelle potentielle pour 5 espèces de parapluie différentes. Dans un deuxième chapitre, nous comparons ces résultats avec les priorités de conservation perçues dans la région. Nous avons organisé un atelier d'une journée avec les parties prenantes impliquées dans l'effort continu de planification de la conservation de la connectivité dans la région et nous avons recueilli des informations sur les caractéristiques du paysage considérées comme des zones prioritaires "centrales" et "de liaison". Nous avons montré l'importance de prendre en compte les changements d'utilisation des terres pour produire un réseau de zones protégées résilient et avons souligné la nécessité d'une approche multipartite dans la définition des scénarios de conservation et l'identification des priorités régionales.}%
\AbstractFr%

@@

\SetAcknowledgeText{
For providing vital guidance and parts of the code, I thank Dr. Bronwyn Rayfield. For providing help with computing resources parts of the code, I thank Dr. Guillaume Larocque. For providing advice on STSIM implementation and code, I thank Dr. Colin Daniel and Dr. Leonardo Frid. I thank Dr. Guillaume Larocque and Dr. Yann Boulanger for their help in providing the LANDIS outputs and editorial help for the associated appendix. \\
\indent I thank all students, staff and organizations involved in the design and realisation of the workshop. I thank Aurélie Sierra for her invaluable guidance and counsel. I thank all students and staff facilitators: Madeleine Gauthier, Mikayla Salmon-Beitel and Violette Bertrand. I thank Geneviève Poirier and Mariève Lafontaine for their participation in the design, planning and organization of the workshop. I also thank Renée Gagnon for her precious help securing a location for the workshop. \\
\indent For providing essential funding for this project, I thank the Fonds de recherche du Québec – Nature et technologies (FRQNT). For providing logistical support I thank Dr. Helen Elina and Mr. Philippe Auzel. \\
\indent For providing key information on land use data, I thank Martin Joly, Marie-Josée Côté and Benoit Jobin. \\
\indent I thank my supervisor, Prof. Andrew Gonzalez, for his support and for believing in my abilities every step of the way. I also thank members of my committee, Prof. Brian Leung and Prof. Elena Bennett for their timely and wise council at every committee meeting. I thank all my fellow grad students and especially Alex Arkilanian for all the help revising proposals, discussion ideas, and providing key support. \\
\indent I thank my mother Laura, my father Philippe, and Talia for their unwavering support. Thank you to Blanka and Peter for sheltering me and putting up with my writing process during the thick of the pandemic. \\
}%
\Acknowledge%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%       THESIS FORMAT AND STYLE       %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\SetLinkName{{Thesis Format}}%
\SetLinkText{This thesis is written in a manuscript-based format.
\\
\\
\textbf{Chapter 1:} Lucet, V. Gonzalez, A. (2020), Integrating Land Use Change Modelling with Connectivity Modelling. %\textit{Journal of Ecographic Informatics} 10 (1), 878887.
\\
\\
\textbf{Chapter 2:} Lucet, V. Gonzalez, A. (2020), Integrating Stakeholders Perceptions of Connectivity Conservation Priorities into a Spatially Explicit Land Use and Connectivity Change Model. %\textit{Journal of Ecographic Informatics} 10 (1), 878887.
\\
\\
}
\Link%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        Contribution of Authors                 %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% A doctoral thesis must clearly state the elements of the thesis that are considered original scholarship and distinct contributions to knowledge.
% Contributions of the student to each chapter must be explicitly stated.
% Contributions of any co-authors to each chapter must be explicitly stated.
\SetContribAuthorsName{{Contribution of Authors}}
\SetContribAuthorsText{\noindent
I am the first author for all chapters and the appendix in this
thesis.
\\
\\
\textbf{Chapter 1:} 
I wrote the manuscript with input from my supervisor.
\\
\\
\textbf{Chapter 2:}
I wrote the manuscript with input from my supervisor.
\\
\\
}%
\ContribAuthors %
\listoffigures %
\listoftables %

@@

\newcommand{\Intro}{%
    \begin{simpleenv}{}{}{}{}%
    \pagestyle{plain}%
  \setboolean{SetDSpace}{false}%
    \GoSingle%
    \begin{QZ@Cent}%
          \bfseries{\ETDIntroName}
      \end{QZ@Cent}%
    \vspace*{0.5in}
      \par%
      \GoDouble%
      \setlength{\parskip}{-2em}
      %\chapter*{\ETDIntroName}%
      \phantomsection\section*{}
      \addcontentsline{toc}{extrachapter}{\ETDIntroName}%
      \ETDIntroText%
    \end{simpleenv}%
    \setboolean{SetDSpace}{true}}%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

LUC is a major cause of habitat loss and fragmentation, and one of the most important threats to biodiversity and ecosystem function worldwide \citep{newbold_global_2015}. It is estimated that LUC was responsible for more than one-third of animal extinctions between 1600 and 1992 \citep{centre_global_1992}. Moreover, a recent report from the IPBES (Intergovernmental Science-Policy Platform on Biodiversity and Ecosystem Services) shows that about about 9\% of all described terrestrial species might suffer from habitat loss to the point that it threatens their long-term persistence \citep{ipbes_summary_2019}. Rarely, however, is habitat loss a complete process; once continuous tracts of habitat are often left as a mosaic of habitat fragments of different sizes separated by land cover with differing degrees of value to the resident fauna and flora.  Habitat fragmentation drives additional loss of diversity and ecosystem services because it reduces the connectivity of the landscape \citep{haddad_habitat_2015}. \\

@@

Connectivity modelling methods depend on the level of organization (individual, population, species or community) and the spatial scale (patch or  landscape) that connectivity is considered. To cover them all is beyond the scope of this introduction, but it is important to replace our choice of methodology in the larger body of foundational work on spatial ecological modelling. This thesis focuses on species level modelling at the landscape scale, and this focus has to be justified. Important efforts in the field of spatial ecological modelling relied on metapopulation theory, island biogeography (IBT), and population genetics. These bodies of theory spurred different approaches to modelling. For example, an IBT approach is focused on predicting diversity (number of species) in island patches \citep{macarthur_theory_1967} and has largely influenced other bodies of work in spat \citep{warren_how_2020}. On the other hand, metapopulation theory is focused on predicting long-term patch occupancy \citep{hanski_habitat_1999, hanski_metapopulation_2000}. Finally, population genetics focuses on predicting gene variation and flow within populations \citep{lewontin_population_1985, charlesworth_population_2017}. Unlike these methods, our goal is to estimate potential animal movement at the species level, over a large spatial and temporal extent. We therefore rely on a more appropriate approach which combines habitat suitability analysis and circuit theory modelling.\\

@@

Deriving insight from these contributions, multiple stakeholders have become mobilized to set connectivity conservation goals for the region. A number of Non-Governmental NGOs have designed corridor networks for their jurisdiction, with varying degrees of inputs from previous scientific work; these include Nature Action Québec (NAQ), Centre de la Nature du Mont Saint Hilaire (CDN), theCentre d'interprétation du milieu écologique du Haut-Richelieu (CIME), and Appalachian Corridors (CA). These associations are now beginning to work together to design science-driven connectivity conservation plans for the whole region, and are in need of science-based decision support tools. They are also concerned with the social acceptability of conservation, and with the resilience of their plans given expected future land use and climate change. \\ \vspace{2em}

@@

The maps produced by previous analyses represent a snapshot of the current state of connectivity in the region. But researchers are developing methods for including future land use and climate change impacts in their analyses. For example, \cite{albert_applying_2017}, used a simple land use and projection from regional climate change models to identify a network of protected habitat robust to climate change for a subset of Montérégie. This was an important step, because ignoring land use change could lead to ill-adapted conservation plans. However, connectivity conservation models rarely include both land use and climate change in their calculations \citep{costanza_landscape_2019}, which and so it remains a limitation in many science-based approaches to  CCP. \\

Similarly, current CCP methods often do not confront the results of the prioritization with the priorities perceived by stakeholders. There is a need for planning tools to allow for this interaction to happen. Those tools need to be able to guide stakeholders through an iterative process of conservation and land use scenario building. Methods are also available to include stakeholder inputs into CCP. Those “participatory research methods” are designed to conduct the research process “with those people whose life-world and meaningful actions are under study” \citep{bergold_participatory_2012}. Those methods often rely on collecting data through a community-driven process during workshops (for an example of a recent local participatory effort in Montérégie see \cite{martins_results_2020}). \\

@@

Next, we introduce the two other key conceptual themes of the thesis: land use change modelling and participatory methods. \\ \vspace{10em}

@@

This thesis therefore makes use of a hybrid modeling approach. We combine this model with scenarios who were derived from a participatory method, which we introduce next. We end with simple predictions as to the results of our modelling effort. \\ \vspace{2em}

\subsection*{\textit{Participatory methods in Connectivity Conservation \\ \vspace{1em}}}

@@

Depending on the scenario, the model generates different forest change dynamics. The Historic scenario assumes no change in forest composition and stands as our control. While the baseline scenario assumes no further warming and status quo forest change dynamics, the RCP 8.5 scenario is one of the most severe climate change scenarios, and the trends observed in the baseline scenario are exacerbated \cite{IPCC}. We also derive two simple land use change scenarios: Business as usual (BAU) and Reforestation. Those two scenarios are meant to represent two extremes in land use change, and it is likely that the most probable trajectories for our landscape will be within those two boundaries. In combination with the climate scenarios, this brings our total scenario number to 6. \\

@@

\subsection*{\textit{Conclusion \\ \vspace{2em}}}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%         English Abstract                        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\SetAbstractEnName{{Abstract}}%
\SetAbstractEnText{Connectivity conservation science, whose goal is to preserve the continuity of habitat throughout a given landscape, proceeds by identifying priority areas given the current configuration of the landscape. However, current connectivity conservation planning methods often do not take into account risks associated with future land use and climate change, and often do not confront the results of the prioritization process with the priorities perceived by stakeholders. In this thesis, we show solutions to those two issues in the context of an ongoing effort of connectivity conservation planning for the region of Montérégie in Southern Québec, Canada. In the first chapter, we built on past work of connectivity modelling using circuit theory in the region and complemented it with land use and climate change modelling that uses a combination of statistical modelling and MCMC-based simulations. Models trained on past land use data were used to project future land use changes and estimate future changes in potential functional connectivity for 5 different umbrella species. In a second chapter, we integrated these results with the perceived conservation priorities in the region. We conducted a day-long workshop with stakeholders involved in the ongoing connectivity conservation planning effort in the region and collected information on landscape features considered as priority areas for connectivity. We translated these results into simple conservation scenarios. We showed the importance of considering land use changes to produce a resilient network of protected areas and highlight the need for a multi-stakeholder approach in the definition of conservation scenarios and the identification of regional priorities.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%         French Abstract                         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\SetAbstractFrName{{Abr\'{e}g\'{e}}}%
\SetAbstractFrText{La science de la conservation de la connectivité, dont le but est de préserver la continuité de l'habitat dans un paysage donné, procède par l'identification des zones prioritaires compte tenu de la configuration actuelle du paysage. Toutefois, les méthodes actuelles de planification de la conservation de la connectivité ne tiennent souvent pas compte des risques liés à l'utilisation future des terres et aux changements climatiques, et ne confrontent souvent pas les résultats du processus de priorisation avec les priorités perçues par les parties prenantes. Dans cette thèse, nous présentons des solutions à ces deux problèmes dans le contexte d'un effort de planification de la conservation de la connectivité pour la région de la Montérégie, dans le sud du Québec, au Canada. Dans le premier chapitre, nous nous sommes appuyés sur les travaux antérieurs de modélisation de la connectivité à l'aide de la théorie des circuits dans la région et nous les avons complétés par une modélisation de l'utilisation des terres et du changement climatique qui utilise une combinaison de modélisation statistique et de simulations de type MCMC. Les modèles formés sur les données d'utilisation des terres passées ont été utilisés pour projeter les changements futurs d'utilisation des terres et estimer les changements futurs de la connectivité fonctionnelle potentielle pour 5 espèces différentes. Dans un deuxième chapitre, nous avons intégré ces résultats aux priorités de conservation perçues dans la région. Nous avons organisé un atelier avec les parties prenantes impliquées dans l'effort de conservation de la connectivité en cours dans la région et nous avons recueilli des informations sur les caractéristiques du paysage considérées comme des zones prioritaires pour la connectivité. Nous avons traduit ces résultats en de simples scénarios de conservation. Nous avons montré l'importance de prendre en compte les changements d'utilisation des terres pour produire un réseau résilient de zones protégées et avons souligné la nécessité d'une approche multipartite dans la définition des scénarios de conservation et l'identification des priorités régionales.}%
\AbstractFr%

@@

\SetAcknowledgeText{
I thank Dr. Bronwyn Rayfield (APEX RMS) for providing vital guidance and parts of the code. I thank Dr. Guillaume Larocque (QCBS) for providing help with computing resources and parts of the code. I thank Dr. Colin Daniel and Dr. Leonardo Frid (APEX RMS) for providing advice on STSIM implementation and code. I thank Dr. Yann Boulanger (NRCAN) for collaborating with the QCBS and providing Dr. Guillaume Larocque with the inputs and guidance needed to generate LANDIS outputs, as well as  Dr. Guillaume Larocque for the editorial help for the associated appendix. I thank all students, staff and organizations involved in the design and realisation of the workshop. I thank Aurélie Sierra for her invaluable guidance and counsel. I thank all students and staff facilitators: Madeleine Gauthier (McGill University), Mikayla Salmon-Beitel and Violette Bertrand (RMN). I thank Geneviève Poirier (CDNMH) and Mariève Lafontaine (NAQ) for their participation in the design, planning and organization of the workshop. I also thank Renée Gagnon (CIME) for her precious help securing a location for the workshop.  For providing essential funding for this project, I thank the FRQNT. For providing logistical support I thank Dr. Helen Elina and Mr. Philippe Auzel (QCBS). For providing key information on land use data, I thank Martin Joly, Marie-Josée Côté and Benoit Jobin (MELCC). I thank my supervisor, Prof. Andrew Gonzalez, for his support and for believing in me at every step of the way. I also thank members of my committee, Prof. Brian Leung and Prof. Elena Bennett for their timely and wise council during the past two years. I thank all my fellow grad students and especially Alex Arkilanian for all their help revising proposals, discussion ideas, and providing the extra push they knew I needed. \\
\indent I thank my mother Laura, my father Philippe, and my dear friend Talia for their unwavering support. I thank Blanka and Peter for sheltering me and putting up with my writing process during the thick of the pandemic. \\
}%
\Acknowledge%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%       THESIS FORMAT AND STYLE       %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\SetLinkName{{Thesis Format}}%
\SetLinkText{This thesis is written in a manuscript-based format.
\\
\\
\textbf{Chapter 1:} Lucet, V. Gonzalez, A. (2020), Integrating Land Use Change Modelling with Connectivity Modelling, a Case Study in Montérégie, Southern Québec. %\textit{Journal of Ecographic Informatics} 10 (1), 878887.
\\
\\
\textbf{Chapter 2:} Lucet, V. Gonzalez, A. (2020), Integrating Stakeholders Perceptions of Connectivity Conservation Priorities into a Spatially Explicit Land Use and Connectivity Change Model. %\textit{Journal of Ecographic Informatics} 10 (1), 878887.
\\
\\
}
\Link%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        Contribution of Authors                 %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% A doctoral thesis must clearly state the elements of the thesis that are considered original scholarship and distinct contributions to knowledge.
% Contributions of the student to each chapter must be explicitly stated.
% Contributions of any co-authors to each chapter must be explicitly stated.
\SetContribAuthorsName{{Contribution of Authors}}
\SetContribAuthorsText{\noindent
I am the first author for all chapters in this thesis.
\\
\\
\textbf{Chapter 1:} 
I wrote the manuscript with input from my supervisor.
\\
\\
\textbf{Chapter 2:}
I wrote the manuscript with input from my supervisor.
\\
\\
}%
\ContribAuthors %
\listoffigures %
\listoftables %

@@

\newcommand{\Intro}{%
    \begin{simpleenv}{}{}{}{}%
    \pagestyle{plain}%
  \setboolean{SetDSpace}{false}%
    \GoSingle%
    \begin{QZ@Cent}%
          \bfseries{\ETDIntroName}
      \end{QZ@Cent}%
    \vspace*{0.5in}
      \par
      \GoDouble%
      \setlength{\parskip}{-2em}
      %\chapter*{\ETDIntroName}%
      \phantomsection\section*{}
      \addcontentsline{toc}{extrachapter}{\ETDIntroName}%
      \ETDIntroText%
    \end{simpleenv}%
    \setboolean{SetDSpace}{true}}%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

LUC is a major cause of habitat loss and fragmentation, and one of the most important threats to biodiversity and ecosystem function worldwide \citep{newbold_global_2015}. It is estimated that LUC was responsible for more than one-third of animal extinctions between 1600 and 1992 \citep{world_conservation_monitoring_centre_global_1992}. Moreover, a recent report from the IPBES (Intergovernmental Science-Policy Platform on Biodiversity and Ecosystem Services) shows that about about 9\% of all described terrestrial species might suffer from habitat loss to the point that it threatens their long-term persistence \citep{ipbes_summary_2019}. Rarely, however, is habitat loss a complete process; once continuous tracts of habitat are often left as a mosaic of habitat fragments of different sizes separated by land cover with differing degrees of value to the resident fauna and flora.  Habitat fragmentation drives additional loss of diversity and ecosystem services because it reduces the connectivity of the landscape \citep{haddad_habitat_2015}. \\

@@

Connectivity modelling methods depend on the level of organization (individual, population, species or community) and the spatial scale (patch or  landscape) that connectivity is considered. To cover them all is beyond the scope of this introduction, but it is important to replace our choice of methodology in the larger body of foundational work on spatial ecological modelling. This thesis focuses on species level modelling at the landscape scale, and this focus has to be justified. Important efforts in the field of spatial ecological modelling relied on metapopulation theory, island biogeography (IBT), and population genetics. These bodies of theory spurred different approaches to modelling. For example, an IBT approach is focused on predicting diversity (number of species) in island patches \citep{macarthur_theory_1967} and has largely influenced other bodies of work in spatial ecology \citep{warren_how_2020}. On the other hand, metapopulation theory is focused on predicting long-term patch occupancy \citep{hanski_habitat_1999, hanski_metapopulation_2000}. Finally, population genetics focuses on predicting gene variation and flow within populations \citep{lewontin_population_1985, charlesworth_population_2017}. Unlike these methods, our goal is to estimate potential animal movement at the species level, over a large spatial and temporal extent. We therefore rely on a more appropriate approach which combines habitat suitability analysis and circuit theory modelling.\\

@@

Deriving insight from these contributions, multiple stakeholders have become mobilized to set connectivity conservation goals for the region. A number of Non-Governmental NGOs have designed corridor networks for their jurisdiction, with varying degrees of inputs from previous scientific work; these include Nature Action Québec (NAQ), Centre de la Nature du Mont Saint Hilaire (CDN), the Centre d'interprétation du milieu écologique du Haut-Richelieu (CIME), and Appalachian Corridors (CA). These associations are now beginning to work together to design science-driven connectivity conservation plans for the whole region, and are in need of science-based decision support tools. They are also concerned with the social acceptability of conservation, and with the resilience of their plans given expected future land use and climate change. \\ \vspace{2em}

@@

Previous analyses have produced a snapshot of the current state of connectivity in the region. But now, researchers are developing methods for including future land use and climate change impacts in their analyses. For example, \cite{albert_applying_2017}, used a simple land use and projection from regional climate change models to identify a network of protected habitat robust to climate change for a subset of Montérégie. This was an important step, because ignoring land use change could lead to ill-adapted conservation plans. However, connectivity conservation models rarely include both land use and climate change in their calculations \citep{costanza_landscape_2019}, which and so it remains a limitation in many science-based approaches to  CCP. \\

In addition, current CCP methods often do not confront the results of the prioritization with the priorities perceived by stakeholders. There is a need for planning tools to allow for this interaction to happen. Those tools need to be able to guide stakeholders through an iterative process of conservation and land use scenario building. Methods are also available to include stakeholder inputs into CCP. Those “participatory research methods” are designed to conduct the research process “with those people whose life-world and meaningful actions are under study” \citep{bergold_participatory_2012}. Those methods often rely on collecting data through a community-driven process during workshops (for an example of a recent local participatory effort in Montérégie see \cite{martins_results_2020}). \\

@@

Next, we introduce the two other key conceptual themes of the thesis: land use change modelling and participatory methods. \\ \vspace{1em}

@@

This thesis therefore makes use of a hybrid modeling approach. We combine this model with scenarios which were derived from participatory methods. Next we introduce those methods and explain this integration. We end this introduction with simple predictions as to the results of our modelling effort. \\ \vspace{2em}

\subsection*{\textit{Participatory methods in CCP and integration with the model \\ \vspace{1em}}}

@@

Depending on the scenario, the model generates different forest change dynamics. The Historic scenario assumes no change in forest composition and stands as our control. While the baseline scenario assumes no further warming and status quo forest change dynamics, the RCP 8.5 scenario is one of the most severe climate change scenarios, and the trends observed in the baseline scenario are exacerbated \cite{ipcc_summary_2013}. We also derive two simple land use change scenarios: Business as usual (BAU) and Reforestation. Those two scenarios are meant to represent two extremes in land use change, and it is likely that the most probable trajectories for our landscape will be within those two boundaries. In combination with the climate scenarios, this brings our total scenario number to 6 (for chapter 1, as conservation scenrios are added in chapter 2). \\

@@

\subsection*{\textit{Conclusion \\ \vspace{2em}}}
\addcontentsline{toc}{chapter}{Conclusion}
